### 2020-11-15 thesis/thesis.tex
fix space

One way to embrace the complexity of the matrix is to carefully look at the relationship between the structure of a landscape and its impact on connectivity and associated ecosystem functions, such as carbon storage or pollination \citep{mitchell_linking_2013}. Both Models \citep{mitchell_strong_2015} and empirical studies \citep{mitchell_forest_2014} have shown that landscape complexity can modify biodiversity, connectivity and ecosystem service supply. While earlier studies focused on single services, more research is looking into how connectivity of forest fragments impact a wide diversity of services\citep{mitchell_forest_2014}. For example, crop heterogeneity is linked to higher biodiversity \citep{sirami_increasing_2019}. Agricultural matrices with smaller average field sizes tend to be more biodiverse \citep{fahrig_farmlands_2015}. These phenomena have been attributed to an increase in connectivity due to the presence of more semi-natural habitats. These contributions are important and should be considered for land use planning. They are appealing for the design of connectivity conservation tools, because they point out clear management scenarios that could be tested through models, and can make use of the increasing availability of high resolution remotely sensed data. \\

>>>>

One way to embrace the complexity of the matrix is to carefully look at the relationship between the structure of a landscape and its impact on connectivity and associated ecosystem functions, such as carbon storage or pollination \citep{mitchell_linking_2013}. Both Models \citep{mitchell_strong_2015} and empirical studies \citep{mitchell_forest_2014} have shown that landscape complexity can modify biodiversity, connectivity and ecosystem service supply. While earlier studies focused on single services, more research is looking into how connectivity of forest fragments impact a wide diversity of services \citep{mitchell_forest_2014}. For example, crop heterogeneity is linked to higher biodiversity \citep{sirami_increasing_2019}. Agricultural matrices with smaller average field sizes tend to be more biodiverse \citep{fahrig_farmlands_2015}. These phenomena have been attributed to an increase in connectivity due to the presence of more semi-natural habitats. These contributions are important and should be considered for land use planning. They are appealing for the design of connectivity conservation tools, because they point out clear management scenarios that could be tested through models, and can make use of the increasing availability of high resolution remotely sensed data. \\
